### 2017-04-01 paper/intro.tex
tweaks on intro

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows: potential, usage,
effectiveness, perception, and tradeoffs.

@@

Each dimension focuses on one aspect of our study.  The dimension
\textbf{potential} measures the potential of parallelization to reduce
testing costs.  In the limit, parallelization would be fruitless if
all projects used short-running test suites or if the bulk of
execution cost was dominated by a relatively small number of tests in
the suite.  The dimension \textbf{effectiveness} measures the observed
impact of parallelization\Comment{~---~when used in selected
  open-source projects~---~} on testing costs.  Intuitively, benefits
are proportional to the cost reduction that parallelization brings.
In the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoff} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  The configuration choice can affect both test cost
and test flakiness.  Flakiness is caused by the non-determinism
resulted from running tests in different
schedulings. Paretto-efficient~\cite{hwang-masud-1979} configurations
can guide future developments in this area.

@@

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
%%  LocalWords:  jenkins API VMs datarace

>>>>

@@

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows: potential, effectiveness,
adoption, and tradeoffs.  Each dimension focuses on one aspect of our
study.  The dimension \textbf{potential} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a
relatively small number of tests in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoff} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  Note that the configuration choice can affect both
test cost and test flakiness, which is caused by the non-determinism
resulted from running tests in different schedulings. Discovering
Pareto-efficient~\cite{hwang-masud-1979} configurations is important
to guide practitioners and future developments in this area.

@@

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
%%  LocalWords:  jenkins API VMs datarace tradeoffs tradeoff Paretto
%%  LocalWords:  schedulings
